Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-02 inspiral_svd.tex
fixed broken tex
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@834 ccdd05d5-56c1-461a-bf98-85f6876523b4
spell check
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@835 ccdd05d5-56c1-461a-bf98-85f6876523b4

\title[LLOID]{Technique for \earlywarning\ detection of compact binary coalescence and its implication for multimessenger astronomy}

@@

\begin{abstract}
The rapid detection of compact binary coalescence with a network of advanced
gravitational-wave detectors will offer a unique opportunity for multimessenger astronomy.  Prompt detection alerts to the astronomical community may make it possible to observe the onset of electromagnetic emission from compact binary coalescence.  We demonstrate a computationally practical analysis strategy that produces early warning triggers even before gravitational radiation from the final merger has arrived at the detectors.  With current rate estimates for the Advanced \LIGO{} design configuration, we should detect $\sim$10 sources earlier than 10 seconds before merger in 1 year of livetime.
\end{abstract}

@@

%\input{analysis}

>>>>

\title[LLOID]{Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy}

@@

\begin{abstract}
The rapid detection of compact binary coalescence with a network of advanced
gravitational-wave detectors will offer a unique opportunity for multi-messenger astronomy.  Prompt detection alerts to the astronomical community may make it possible to observe the onset of electromagnetic emission from compact binary coalescence.  We demonstrate a computationally practical analysis strategy that produces early warning triggers even before gravitational radiation from the final merger has arrived at the detectors.  With current rate estimates for the Advanced \LIGO{} design configuration, we should detect $\sim$10 sources earlier than 10 seconds before merger in 1 year of live time.
\end{abstract}

@@

\input{analysis}
